Subtle Gestures with the J!NS MEME

### 2021-08-17 Paper/paper.tex
Use proper citation for GitHub links

\subsection{Tools for Recording and Labelling}
% TODO include the links via BibTeX
To use the J!ns Meme, we first had to interface with it. The interface would have to allow
both recording and streaming the data from the smartglasses, perferrably.
The J!ns Meme's sensor data can be read either via an iOS, Android or macOS app
or via a Windows app, with the latter requiring a custom bluetooth dongle. For
initial gesture evaluation we used the Android app, but since we set out to have
live classification with the potential to control your computer, and only Windows
machines were available, we chose the Windows app J!ns Meme DataLogger
[https://github.com/jins-meme/ES\_R-DataLogger-for-Windows]. A development kit was
available for Android, macOS and Windows as well
[https://github.com/jins-meme/ES\_R-Development-Kit], but it did not eliminate the
need for the bluetooth dongle on Windows and only implied a bigger overhead for us,
since the DataLogger can both record and forward the J!ns Meme's sensor data to a
file and a TCP port, respectively.

%TODO check correctness, this is from memory alone
The J!ns Meme DataLogger supplies eleven values per cycle, three of which are the
accelerometers' data and the remaining eight being processed EOG data.
Notably, we observed that we had different values available via the Android app
[https://github.com/jins-meme/ES\_R-DataLogger-for-Android]. Namely
there were gyroscope values, albeit they were constantly zero, and less EOG data fields.
We found this behavior to be the same on all J!ns Meme smartglasses and Android phones
we had available, but are not certain if it is intended behavior.

>>>>

\subsection{Tools for Recording and Labelling}
% TODO include the links via BibTeX
To use the J!ns Meme, we first had to interface with it. The interface would have to allow
both recording and streaming the data from the smartglasses, perferrably.
The J!ns Meme's sensor data can be read either via an iOS, Android or macOS app
or via a Windows app, with the latter requiring a custom bluetooth dongle. For
initial gesture evaluation we used the Android app, but since we set out to have
live classification with the potential to control your computer, and only Windows
machines were available, we chose the Windows app J!ns Meme DataLogger
\cite{jinsMemeDataLoggerWin}. A software development kit is available for Android, macOS
and Windows as well \cite{jinsMemeSDK}, but it did not eliminate the
need for the bluetooth dongle on Windows and only implied a bigger overhead for us,
since the DataLogger can both record and forward the J!ns Meme's sensor data to a
file and a TCP port, respectively.

%TODO check correctness, this is from memory alone
The J!ns Meme DataLogger supplies eleven values per cycle, three of which are the
accelerometers' data and the remaining eight being processed EOG data.
Notably, we observed that we had different values available via the Android app
\cite{jinsMemeDataLoggerAndroid}. Namely there were gyroscope values, albeit they
were constantly zero, and less EOG data fields.
We found this behavior to be the same on all J!ns Meme smartglasses and Android phones
we had available, but are not certain if it is intended behavior.
